Report for the Deep Learning Course Assignment 3

### 2016-12-16 practical_3/report/report_methenitis.tex
update report

classif = OneVsRestClassifier(SVC(kernel='linear'))
classif.fit(features[train_set], batch_y[train_set]
classif.score(features[test_set], batch_y[test_set]
\end{verbatim}
Here, the reported accuracy of the one-vs-classifiers on the test set:
\begin{itemize}
\item Accuracy with flatten features: $0.6306$.
\item Accuracy with fc1 features: $0.$.
\item Accuracy with fc2 features: $0.$.
\end{itemize}
It is natural that the accuracy is higher for later layers.
As it was earlier $fc2$ layer can distinguish better features of different classes.

@@

x1 = self._images[random_index]
x2 = self._images[matches[:n_correct]]
x2 = np.vstack((x2, self._images[mismatches[n_correct:]]))
labels = np.hstack((np.ones((n_correct)), np.zeros((batch_size-n_correct))))
\end{verbatim}
\end{tiny}
generates batches of random pairs of images respecting the \texttt{fraction} of same label images.
The resulted batch 
\begin{verbatim}
      X_1            X_2               Y
| image_cl1_10, image_cl1_50   | -->   | 1 |
| image_cl4_17, image_cl4_234  | -->   | 1 |
| image_cl8_654, image_cl8_14  | -->   | 1 |
| image_cl8_66, image_cl6_234  | -->   | 0 |
|      .            .          | -->   | 0 |
|      .            .          | -->   | 0 |
|      .            .          | -->   | 0 |
| image_cl2_327, image_cl6_234 | -->   | 0 |
\end{verbatim}
\end{itemize}

@@

 \begin{figure}[h!]
\centering
\includegraphics[width=5.2cm]{graph.png}
\caption{Graph for the task 3 of the assignment, the final three layers of convnet were used. Note the stop gradient operation, where we don't want to update the pre-trained weights.}
\label{fig:features}
\end{figure}

>>>>

classif = OneVsRestClassifier(SVC(kernel='linear'))
classif.fit(features[train_set], batch_y[train_set]
classif.score(features[test_set], batch_y[test_set]
\end{verbatim}
Here, the reported accuracy\footnote{The accuracy is reported to half of the test set ($5000$ random samples without replacement due to slow training of the OneVsRestClassifier		)} of the one-vs-classifiers on the test set:
\begin{itemize}
\item Accuracy with flatten features: $0.59$.
\item Accuracy with fc1 features: $0.59$.
\item Accuracy with fc2 features: $0.703$.
\end{itemize}
It is natural that the accuracy is higher for later layers.
As it was earlier $fc2$ layer can distinguish better features of different classes.

@@

x1 = self._images[random_index]
x2 = self._images[matches[:n_correct]]
x2 = np.vstack((x2, self._images[mismatches[n_correct:]]))
labels = np.hstack((np.ones((n_correct)), np.zeros((batch_size-n_correct))))
\end{verbatim}
\end{tiny}
generates batches of random pairs of images respecting the \texttt{fraction} of same label images.
The resulted batch 
\begin{verbatim}
      X_1            X_2               Y
| image_cl1_10, image_cl1_50   | -->   | 1 |
| image_cl4_17, image_cl4_234  | -->   | 1 |
| image_cl8_654, image_cl8_14  | -->   | 1 |
| image_cl8_66, image_cl6_234  | -->   | 0 |
|      .            .          | -->   | 0 |
|      .            .          | -->   | 0 |
|      .            .          | -->   | 0 |
| image_cl2_327, image_cl6_234 | -->   | 0 |
\end{verbatim}
Is is expected that classes are uniformly picked in expectation given the random sampling. Given the default way of selecting training batches training among classes is not guarranteed to be uniform.
Later we see that the alternative way of creating batches achieves the highest accuracy in the end of training using the one-vs-rest classifier.
\end{itemize}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=5.2cm]{graph.png}
\caption{Graph for the task 3 of the assignment, the final three layers of convnet were used. Note the stop gradient operation, where we don't want to update the pre-trained weights.}
\label{fig:graph}
\end{figure}

\subsection{Feature Extraction}

\begin{figure}[h!]
\centering
\includegraphics[width=12.2cm]{acc-transfer.png}\	
\includegraphics[width=12.2cm]{loss-transfer.png}
\caption{}
\label{fig:extra}
\end{figure}

\subsection{Retraining}

\begin{figure}[h!]
\centering
\includegraphics[width=12.2cm]{acc-retrain.png}\	
\includegraphics[width=12.2cm]{loss-retrain.png}
\caption{}
\label{fig:retrain}
\end{figure}

\subsubsection{Refining}
